Structured Classification for Inverse Reinforcement Learning

### 2012-06-27 klein2012/main.tex
Last changes before EWRL12

%\documentclass[gray]{jmlr} % test grayscale version
\documentclass[tablecaption=bottom]{jmlr}

@@

 % Two authors with the same address
  \author{\Name{Paper under review at ICML}\thanks{No author name provided so as not to breach ICML's double blind process}}

>>>>

%\documentclass[gray]{jmlr} % test grayscale version
\documentclass[tablecaption=bottom]{jmlr}
%\usepackage{marvosym}

@@

 % Two authors with the same address

\author{\Name{{\'E}douard Klein$^{\dag\ddag}$}, \Name{Bilal Piot$^{\dag\textrm{*}}$}, \Name{Matthieu Geist$^\dag$}, \Name{Olivier Pietquin$^{\dag\textrm{*}}$}\\
\Email{firstname.lastname@supelec.fr}\\
\addr $\dag$ {\'E}quipe IMS/MaLIS (Sup{\'e}lec), $\ddag$ {\'E}quipe ABC UMR 7503 (Loria-CNRS), * UMI 2958 (GeorgiaTech-CNRS).
}
